Risk Perceptions for Wearable Devices

### 2015-03-07 tex-inputs/results-techrank.tex
Kills orphans dead.

Of the wearable technologies, privacy-invasive ones were perceived to be risky. The riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10''). The differences in risk between the different wearable-related technologies, were not tested for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible. Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.

Participants were prompted to rate technologies with respect to all considerations (see ~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life. Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk. Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.

These perceptions of the most risky or beneficial technologies may not be reflective of actual risks or benefits. However, they do reflect the general public's exposure to these technologies and their perceptions, they also show that people perceive specific risks and benefits. We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities of these technologies or how they could be used. We suspect that performing this experiment longitudinally may yield more interesting results, as these technologies become more and more pervasive (and therefore more familiar to participants).

>>>>

Of the wearable technologies, the riskiest technologies included facial recognition, the Internet, and discrete cameras, whereas the remainder of the technologies were seen as having minimal, equivalent risk levels (i.e., a median of ``10''). We did not test the differences in risk between the different wearable-related technologies for statistical significance, but given their minimal spread compared to the calibration options, the differences appears to be negligible. Interestingly, privacy risks were perceived as being comparable to physical risks; for instance, the capacity for facial detection on a wearable device was perceived as being almost as risky as interacting with a lawnmower.

Participants were prompted to rate technologies with respect to all considerations (see Appendix~\ref{sec:prompt}), including risk of physical harm to bystanders, financial cost, distress, misuse, or impact on public, personal, and private life. Participants may have still evaluated the risks with an emphasis toward physical risk and without an emphasis on privacy risk. Among the five presented options, the wearable-related one is the only one without some physical risk scenario, and physical risk is a clear, tangible risk.

We examined participants' perceptions, and therefore responses may not be reflective of actual risks or benefits. However, they also reflect the general public's exposure to these technologies and show that people perceive specific risks and benefits. We suspect that the similarity in assessments between the various wearable technologies are because most people are not consciously aware of the possibilities and that performing this experiment longitudinally may yield more interesting results, as these technologies become pervasive (and more familiar to participants).
